Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 

### 2022-12-27 scripts/manuscript/manuscript_draft.qmd
SE for age adjusted rates

---
title: "Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 "
format: docx
editor: visual
bibliography: references.bib
csl: ama.csl
---
```{r}
library(gtsummary)
library(tidyverse)
library(patchwork)
library(targets)
library(gt)

@@

We used data from the Medical Expenditure Panel Survey (MEPS) from years 2008 - 2020. Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS). The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage. This survey also contains information on patient demographics, socioeconomics, and via the Diabetes Care Survey (DCS), information on diabetes preventive care practices. The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.

The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design, including clustering and stratification.

@@

# Tables
```{r}
# tar_load(age_adjusted_stats)
# age_adjusted_stats %>% 
#   #filter(stratifier != 'age') %>% 
#   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
#   pivot_wider(
#     id_cols = c(stratifier, variable, var_label, strata),
#     names_from = year,
#     values_from = age_adjusted_prop
#   ) %>% 
#   group_by(stratifier, strata) %>%
#   select(stratifier, var_label, `2008`:`2020`) %>%
#   gt() %>% 
#   fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
#   gtsave('table_one.docx')
```

>>>>

---
title: "Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 "
format: docx
editor: visual
bibliography: references.bib
csl: ama.csl
---

```{r}
library(gtsummary)
library(tidyverse)
library(patchwork)
library(targets)
library(gt)

@@

We used data from the Medical Expenditure Panel Survey (MEPS) from years 2008 - 2020. Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS). The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage. This survey also contains information on patient demographics, socioeconomics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices. The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.

The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report. We used a weighted population of XXX in this analysis. Our analysis is adjusted for the complex survey design, including clustering and stratification. Reported values for the proportions of different groups receiving recommended preventive care practices are age-adjusted.

@@

# Tables

```{r}
# tar_load(age_adjusted_stats)
# age_adjusted_stats %>% 
#   #filter(stratifier != 'age') %>% 
#   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
#   pivot_wider(
#     id_cols = c(stratifier, variable, var_label, strata),
#     names_from = year,
#     values_from = age_adjusted_prop
#   ) %>% 
#   group_by(stratifier, strata) %>%
#   select(stratifier, var_label, `2008`:`2020`) %>%
#   gt() %>% 
#   fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
#   gtsave('table_one.docx')
```
